Rule learning from classified temporal data

### 2016-08-29 Travis/main.tex
consisstent notation

\title{Detecting TravisCI Misconfiguration}
\subtitle{Plan of Attack}

\authorinfo{Name1}           {Affiliation1}           {Email1}
\authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}

@@

\begin{abstract}
We can detect TravisCI misconfigurations using ConfigC.
\end{abstract}

@@

@@

The language of TravisCI configuration files can likely be handled by ConfigC.
ConfigC works on languages with shallow parse trees, and most of the .travis.yml files is shallow.
However, because .travis.yml allows for bash scripts, some error may be out of scope.
We want to identify the frequency of the types of errors - if too many are related to poorly formed bash scripts, a naive application of ConfigC will not suffice.

@@

An intersting extension to ConfigC on a theortical side is to look at the temporal relations between commits.
The key observation is that with each commit that changes the build status, we can learn highly localized information about our model.

The first step is to build an intermediate representation of the data we will learn.
For the sake of efficiency, this data must be structured as a shallow tree.
While the travis.yml file can be taken verbatim, we must use a simplification of the program code.
Since we are only intrested in the parts of the program effecting build status, we should extract the imported libraries as a list.
We will call this summary $S_t$, a simplified representation of the program which contains only the information relevant to the learning process.
The subscript is a tag based on the ordered commit history.
To handle branches, add a superscript to indicate the branch, and restart the counter on a branch - merging should be handled easily (not exactly sure how yet).

@@

We will denote the build status of $S_t$ with $B(S_t)$.
In this application, we consider only the passing and erroring build status, denoted $P$, and $E$ respectivly.
All status that are not \verb|error|, as defined by the Travis API, will be included as passing.
For brevity, we denote sequences of build statuses with the following notation:

$S(P_t)=P \land S(P_{t+1})=E \implies S(P_{t,t+1}) = PE$

@@

$S(P_t)=P \implies \forall r \in M(P_t), r \notin Br$

@@

We then can combine all these formulas with conjunctions and send it to an SMT solver and magically get an answer.
While exstential set operations can be expensive in general for an SMT solver, in our application this is not the case.
Because these sets will be small thanks to the practice of making incremental commits when using source control, these operations will be fairly cheap.
In fact, the above implication generalizes to $P_{t,t+n}$, but for efficency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is managably small.
The definition of small here remains to be experimentally determined.

>>>>

\title{Rule learning from classified temporal data}
\subtitle{Plan of Attack}

\authorinfo{Mark Santolucito}           {Yale University}           {mark.santolucito@yale.edu}
\authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}

@@

\begin{abstract}
Rule based classification is an effective machine learning technique that yields low misclassification rates.
However, building a rule based system requires manual creation of large databases of logical constraints.
We present a method to generate rule based systems from temporally structured data.
As an demonstration of this algorithm, we implement a learner to automatically generate constraints for the TravisCI testing framework.
The algorithm runs over Github commit histories to generate logical constraints that allow us to detect potential build errors without actually building, saving valuable programmer and server time.
\end{abstract}

@@

\section{Introduction}

@@

The language of TravisCI configuration files can likely be handled by ConfigC.
ConfigC works on languages with shallow parse trees, and most of the .travis.yml files is shallow.
However, because .travis.yml allows for bash scripts, some error may be out of scope.
We want to identify the frequency of the types of errors - if too many are related to poorly formed bash scripts, a naïve application of ConfigC will not suffice.

@@

An interesting extension to ConfigC on a theoretical side is to look at the temporal relations between commits.
The key observation is that with each commit that changes the build status, we can learn highly localized information about our model.

The first step is to build an intermediate representation of the data we will learn.
For the sake of efficiency, this data must be structured as a shallow tree.
While the travis.yml file can be taken verbatim, we must use a simplification of the program code.
Since we are only interested in the parts of the program effecting build status, we should extract the imported libraries as a list.
We will call this program summary $P_t$, a simplified representation of the program which contains only the information relevant to the learning process.
The subscript is a tag based on the ordered commit history.
To handle branches, add a superscript to indicate the branch, and restart the counter on a branch - merging should be handled easily (not exactly sure how yet).

@@

We will denote the build status of $P_t$ with $B(P_t)$.
In this application, we consider only the passing and erroring build status, denoted $Pass$, and $Err$ respectively.
All status that are not \verb|error|, as defined by the Travis API, will be included as passing.
For brevity, we denote sequences of build statuses with the following notation:

$S(P_t)=Pass \land S(P_{t+1})=Err \implies S(P_{t,t+1}) = PE$

@@

$S(P_t)=Pass \implies \forall r \in M(P_t), r \notin Br$

@@

We then can combine all these formulas with conjunctions and send it to an SMT solver and magically get an answer.
While existential set operations can be expensive in general for an SMT solver, in our application this is not the case.
Thanks to the practice of making incremental commits when using source control, these sets will be small and the SMT will be fairly cheap.
In fact, the above implication generalizes to $P_{t,t+n}$, but for efficiency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is manageably small.
The definition of small here remains to be experimentally determined.
